\documentclass[a4paper]{article}
\usepackage{tabularx}
\usepackage{ae}
\usepackage[T1]{fontenc}
\usepackage{CV}
\usepackage[left=1.5cm,top=1cm,right=1.5cm,nohead,nofoot]{geometry}
\title{My Resume}
\author{Siddharth S Pai}
\begin{document}
\pagestyle{empty}
\begin{center}

\Large
\textsc{SIDDHARTH S PAI}
\end{center}
\vspace{1.2\baselineskip}
\begin{flushleft}
B.Tech Computer Science and Engineering\\Federal Institute of Science and Technology [FISAT],Angamaly,Kerala\\
Phone (Mobile 1): 8547307359\\
Phone (Mobile 2): 9567716247\\
Email: siddhartpai@gmail.com \\
\end{flushleft}

\section{Objective}
\begin{flushleft}
Helping people.
\end{flushleft}


\section{Education Qualification}
\begin{CV}
\item[2009 -- 2013] B.Tech Computer Science and Engineering \\
Institution : Federal Institute Of Science And Technology, Angamaly ,Kerala \\
University : MG University \\
Status : 56 \% 
\item[2007 -- 2009] Class XII\\
Institution : Bharatiya Vidya Bhavan,Kannur, Kerala\\
Board : CBSE\\
Status : 86.6 \%
\item[2006 -- 2007] Class X\\
Institution : Bharatiya Vidya Bhavan, Kannur , Kerala\\ 
Board : Kerala State Board\\
Status : 85.0 \%
\end{CV}


\section{Project Summary}
\begin{tabular}{r|p{15cm}}
\emph{B.Tech} & Mini Project \\
\textsc{2012} & \emph{Robo Artist} \\
& \normalsize{This project involved the creation of 4 robots to draw a single image on paper. This was acheived by creating four robots which would eachplot points on paper. The control of the robots was done via a python interface. The data was sent via Bluetooth. Image processing was done using Octave. 
}
\\
\multicolumn{2}{c}{}
\end{tabular}

\begin{tabular}{r|p{15cm}}
\emph{B.Tech} & Main Project \\
\textsc{2013} & \emph{SAT Solver} \\
& \normalsize{This project was done to focus on splitting work and how fast work can be done if it was split into different processes. We attempted to solve a SAT Problem by splitting the work among different processes and then bruteforcing it to acheive our goal. 
}
\\
\multicolumn{2}{c}{}
\end{tabular}

\section{Technical Expertise}
\begin{itemize}
\item Hardware \indent \ \ \ \ \ \  \  \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ :  8085 , Arduino
\item Programming Languages \indent \ \ \ \ : Bash Scripting , C , C++ ,  Java ,  PHP , Python  , SQL
\item Operating System \indent \ \ \ \ \ \ \  \ \ \ \ \ \ : GNU/Linux (Arch, Debian , Fedora ,Ubuntu ), Windows 
\item Application Packages \indent \ \ \ \ \ \ \  \ \ : Audacity , LaTeX ,  MS Office, Open Office
\item Favourite Editors \indent \ \ \ \ \ \ \ \ \ \ \ \ \ \ :  Nano, Geany , Emacs , Sublime Text
\end{itemize}

\section{Professional Membership}
\begin{itemize}
\item FISAT Free Software Cell(FFSC)
\end{itemize}


\section{Extracurricular Achievements}
\begin{itemize}
\item $ 1^{st} $ in Declamation in Intra School Cultural Meet, Kannur.
\end{itemize}

\section{Positions of Responsibility}
\begin{itemize}
\item	Head for Online Registration during Inter College Fest Bharatham.
\item	Execom Member of FFSC .
\item	Was a part of the team involved in "One Million Code" .
\item	Head for Registration during Intra College Fest Arangu.
\item	Event Head for "Tableau" during Intra College Fest Arangu.
\item	Volunteer for ICEFOSS 2010 and 2011
\item	Volunteer for Fisat Science Congress.
\item	Was a Project Leader in School .
\item	House Captain in School.

\end{itemize}

\section{Hobbies}
\begin{itemize}
\item	Watching documentaries and movies .
\item	Reading Novels ,listening to music .
\item	Coding.
\end{itemize}


\section{Personal Details}
\begin{flushleft}
\begin{tabular}{ll}
\indent \ \ \ Gender :  Male \\
\indent  \ \ \   Nationality : Indian\\
\indent   \ \  \ Date of birth : 24 April 1992 \\
\indent \ \ \   Languages known  : English,Konkani, Malayalam,Hindi
\end{tabular}
\end{flushleft}

\section{Reference}

\textbf{Mr. Mahesh C},  System Analyst cum Software Engineer\\
\indent  Federal Institute of  Science And Technology \\
\indent mahesh.fisat@gmail.com \\

\textbf{Mr. Unni Kartha G} , Placement Co-ordinator  and Head of the Department [Civil Engineering] \\ 
\indent Federal Institute of Science and Technology\\ 
\indent unnikartha@gmail.com 

\section{Declaration}
\indent \ \ I hereby declare that the above furnished information is true to my knowledge and belief. \\ \\ \\
\vspace{5\baselineskip}
\indent \textbf {09.02.2013} \indent \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \textbf{Signature}

\end{document}